Interacting Classical Gas

### 2016-11-01 Interacting Classical Gas_Zhiyu_APS.tex
Nov1 APS's PRE format, tex

\documentclass[aps,pre,twocolumn
,groupedaddress]{revtex4-1}
%\documentclass[a4paper,onecolumn,12pt]{article}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{bm}
 \begin{document}
 \title{Interacting Classical Gas}
 \author{Zhiyu}
 \affiliation{Fudan University, Shanghai, China}

@@

\newpage
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000_pre.eps}
\caption{Energy distribution, N=5, F0=10000}
\label{fig:thermalization8}

\includegraphics[scale=0.47]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=10_E=1000_edit.eps}
\caption{Energy distribution, N=10, E=1000 {\color{red}{Run with N=10 F0=10000 to substitute this one}} }
\label{fig:thermalization9}

\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=20_F0=10000_pre.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

@@

\section{Relaxation in Phase-space}

@@

All our discussion before is based on the approximation that every particle collide with each other once in one period. But this is hardly true in reality. If the number of collision in every period is taken into account, these two regime looks even more different: In ``bouncing regime", the average precession speed is significant, (see Fig.\ref{fig:Breathingfrequency4}), which means each collision cause a finite precession. The fluctuation of the number of collision one particle has in each period will contribute to the divergence of their phase angles. On the contrary, in ``passing regime", (see Fig.\ref{fig:Breathingfrequency4}), the breathing frequency is close to 2, which means the average effect of collision create zero precession speed. As a result, even though the number of collision is not a constant, it has no effect on average whether one particle collide more or less in one period.

@@

\subsubsection{Shape of Distribution in Phase-space}
If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse. If the phase of oscillation is completely random, the cloud should be isotropic in phase space. In view of this, we defined a shape factor S:
\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively. a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
S=1 for line-shape distribution, S=0 for circular distribution.
The time evolution of S will probably show how fast the distribution ``forget" its initial shape.

@@

\centering
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
\caption{N=50, E=20000, F0=10000 ,t=1500}
\label{fig:relaxationPS6}
\end{figure}

\newpage
\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
\begin{figure}[hbtp]
\begin{center}
\subfigure[$E=3E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
\end{minipage}
}
\subfigure[$E=2E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
\end{minipage}
}
\subfigure[$E=1E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}

@@

\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
\end{minipage}
}
\end{center}
\end{figure}

\newpage
\subsection{Lyapunov Exponents(unfinished)}
Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space. The largest Lyapunov exponents (LLE) reflects  the time scale that system lose its memory in phase-space. We will measure the LLEs along our trajectory and plot its distribution.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=3000_2.eps}
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_Energy_F0=1000_E=3000_2.eps} 
\caption{N=5, F0=1000, E=3000, Gaussian interaction}
\label{fig:LLEexample1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=10000_1.eps}
\caption{N=5, F0=1000, E=10000, Gaussian interaction}
\label{fig:LLEexample2}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=100000_1.eps}
\caption{N=5, F0=1000, E=100000, Gaussian interaction}
\label{fig:LLEexample3}
\end{figure}

Fig.\ref{fig:LLEexample1}, fig.\ref{fig:LLEexample2} and fig.\ref{fig:LLEexample3} serve as examples showing the way I measure LLE: I integrate and average the LLE along the trajectory, usually over 100-1000 time unit, the LLE converge to certain stable value, and then I start another LLE measurement. \textbf{From the examples above, one may judge how good the convergence is and how big the error of LLE measurement can be.}

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_27.eps}
\caption{LLE distribution for N=5, F0=1000, scan E. (It seems that MATLAB has difficulty changing .fig into .eps files. To get rid of the annoying white lines you may open this figure in MATLAB with .fig format.)}
\label{fig:LLEdistribution1}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{Interacting Classical Gas_Zhiyu_bib.bib}

>>>>

\documentclass[aps,pre,twocolumn
,groupedaddress]{revtex4-1}
%\documentclass[a4paper,onecolumn,12pt]{article}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{bm}
   \usepackage[colorlinks,
            linkcolor=red,
            anchorcolor=blue,
            citecolor=green
            ]{hyperref}
 \begin{document}
 \title{Interacting Classical Gas}
 \author{Zhiyu}
 \affiliation{Fudan University, Shanghai, China}

@@

\newpage
\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/distribution_at_N=5_F0=10000_pre.eps}
%\caption{Energy distribution, N=5, F0=10000}
%\label{fig:thermalization8}

\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=10_F=10000_pre.eps}
\caption{Energy distribution, N=10, F0=10000}
\label{fig:thermalization9}

\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/11_1_boltzmann_N=20_F=10000_pre.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

@@

\subsection{Relaxation in Phase-space}

@@

All our discussion before is based on the approximation that every particle collide with each other once in one period. But this is hardly true in reality. If the number of collision in every period is taken into account, these two regime looks even more different: In ``bouncing regime", the average precession speed is significant, (see Fig.\ref{fig:Breathingfrequency4}), which means each collision cause a finite precession. The fluctuation of the number of collision one particle has in each period will contribute to the divergence of their phase angles. On the contrary, in ``passing regime", (see Fig.\ref{fig:Breathingfrequency4}), the breathing frequency is close to 2, which means the average effect of collision create zero precession speed. As a result, even though the number of collision is not a constant, it has on average no effect whether one particle collide more or less in one period.

To directly check this argument, we can inspect the frequency spectrum of $R(t)$. As is shown in FIG.\ref{fig:frequencyspectrum}, when $F_0$ is very small (red curve), the peak is very sharp and peak frequency is exactly 2. When $F_0$ goes far beyond the threshold value of $\frac{E}{N\sigma}$ (blue, purple, pink, etc.), the peak becomes a wide distribution with a peak value deviated far from 2, which lead to  fast thermalization according to our argument before.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_spectrum_N=10_E=1000_pre.eps}
\caption{Frequency spectrum, measured over $10^4$ time units.\label{fig:frequencyspectrum}}
\end{figure}

\subsection{Lyapunov Exponents}
To see the time scale of ``thermalization" and ``relaxation" more systemetically, we may measure the Lyapunov Exponents. Lyapunov exponents(LE) describes how fast one orbit diverge from its nearby orbits in phase-space. The largest Lyapunov exponents (LLE) reflects  the time scale that system lose its memory in phase-space. We will measure the LLEs along our trajectory and plot its distribution.

\begin{comment}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=3000_2.eps}
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_Energy_F0=1000_E=3000_2.eps} 
\caption{N=5, F0=1000, E=3000, Gaussian interaction}
\label{fig:LLEexample1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=10000_1.eps}
\caption{N=5, F0=1000, E=10000, Gaussian interaction}
\label{fig:LLEexample2}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{D:/matlab2016/MolecularDynamics/figure/latexpic/C_N=5_LLEevolution_F0=1000_E=100000_1.eps}
\caption{N=5, F0=1000, E=100000, Gaussian interaction}
\label{fig:LLEexample3}
\end{figure}

Fig.\ref{fig:LLEexample1}, fig.\ref{fig:LLEexample2} and fig.\ref{fig:LLEexample3} serve as examples showing the way I measure LLE: I integrate and average the LLE along the trajectory, usually over 100-1000 time unit, the LLE converge to certain stable value, and then I start another LLE measurement. \textbf{From the examples above, one may judge how good the convergence is and how big the error of LLE measurement can be.}
\end{comment}

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_scanE_9_27_pre_screenshot.png}
\caption{LLE distribution for N=5, F0=1000, scan E.}
\label{fig:LLEdistribution1}
\end{figure}

@@

\subsection{{\color{red}{Shape of Distribution in Phase-space}}}
If the oscillating phases of particles are highly correlated, for example, initial state with zero velocity, the shape of cloud will be a thin ellipse. If the phase of oscillation is completely random, the cloud should be isotropic in phase space. In view of this, we defined a shape factor S:
\\$S=\frac{a-b}{a+b}$, where a and b are long axis and short axis of inertia ellipse in phase space respectively. a,b can be calculated by diagonalizing the inertia matrices I: $I_{xx}=\sum{x^2}, I_{xp}=I_{px}=\sum{xp},I_{pp}=\sum{p^2}$
S=1 for line-shape distribution, S=0 for circular distribution.
The time evolution of S will probably show how fast the distribution ``forget" its initial shape.

\begin{comment}
\begin{figure}[hbtp]

@@

\centering
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1.eps}
\includegraphics[scale=0.8]{D:/matlab2016/MolecularDynamics/figure/latexpic/shapefactor_t=1500_N=50_F10000_E20000_S=1_average.eps} 
\caption{N=50, E=20000, F0=10000 ,t=1500}
\label{fig:relaxationPS6}
\end{figure}
\end{comment}

\begin{comment}
%\subsection{Correspondence between energy distribution, behaviour of shape-factor and oscillation of R(t)}
\begin{figure}[hbtp]
\begin{center}
\subfigure[$E=3E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=3E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=3E5.eps}   
\end{minipage}
}
\subfigure[$E=2E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_single-particle-Energy_relaxed_N=20_F0=1E4_E=2E5.eps}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=2E5.eps}   
\end{minipage}
}
\subfigure[$E=1E5$]{
\begin{minipage}[n]{0.4\textwidth}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Energy_relaxed_N=20_F0=1E4_E=1E5.eps}

@@

\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/example_Shapeav_relaxed_N=20_F0=1E4_E=5E4.eps}   
\end{minipage}
}
\end{center}
\end{figure}
\end{comment}

\newpage

\section{Conclusion}

@@

\newpage
\renewcommand\refname{Reference}
%\bibliographystyle{plain}
\bibliography{E:/Reference/mybib}
